Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-04-13 src/tex/ms.tex
Clean up figure labels.

As a visual check for outliers, we reconsider the set of measurements in Fig.~\ref{fig:violin_kappa} in light of the hierarchical result for $\mu$ and $\sigma$ in Fig.~\ref{fig:corner_Gaussian}, including GW200129 (blue curve).
This amounts to reweighting the $\kappa$ posterior for each event under a population prior marginalized over $\mu$ and $\sigma$, conditional on the measurements from all other events \cite{Callister:T2100301}.
Figure \ref{fig:corner_Gaussian} does not show evidence for any of the events being in obvious tension with the population, even though the GW170818 curve stands out from the rest due to its higher support for $\kappa > 0$.
This feature appears to offset a few other events which tend to favor $\kappa < 0$.
The interaction between these distributions leads to a hyperposterior that is fully consistent with $\mu = 0$ while offering some support for $\sigma > 0$ (Fig.~\ref{fig:corner_Gaussian}).
Future observations will determine whether there is truly evidence for a nonvanishing variance in this population.

@@

Having established that the collection of detections is globally consistent with $\kappa=0$, here we focus on four events whose $\kappa$ posteriors stand out in Fig.~\ref{fig:posterior_kappa}: GW170818, GW190521 and GW200129.
When considered in isolation, the first of these is the unimodal event with the most significant support for nonzero $\kappa$, the third is the most extreme representative of a class of events with bimodal $\kappa$ posteriors, and the third shows signs of potential noise anomalies.
Through these examples, we elucidate some of the interactions between $\kappa$ and the source luminosity distance, inclination and spin parameters.

>>>>

As a visual check for outliers, we reconsider the set of measurements in Fig.~\ref{fig:violin_kappa} in light of the hierarchical result for $\mu$ and $\sigma$ in Fig.~\ref{fig:corner_Gaussian}, including GW200129 (blue curve).
This amounts to reweighting the $\kappa$ posterior for each event under a population prior marginalized over $\mu$ and $\sigma$, conditional on the measurements from all other events \cite{Callister:T2100301}.
The result in Figure \ref{fig:reweighted_kappa} does not show evidence for any of the events being in obvious tension with the population, even though the GW170818 curve stands out from the rest due to its higher support for $\kappa > 0$.
This feature appears to offset a few other events which tend to favor $\kappa < 0$.
The interaction between these distributions leads to a hyperposterior that is fully consistent with $\mu = 0$ while offering some support for $\sigma > 0$ (Fig.~\ref{fig:corner_Gaussian}).
Future observations will determine whether there is truly evidence for a nonvanishing variance in this population.

@@

Having established that the collection of detections is globally consistent with $\kappa=0$, here we focus on four events whose $\kappa$ posteriors stand out in Fig.~\ref{fig:violin_kappa}: GW170818, GW190521 and GW200129.
When considered in isolation, the first of these is the unimodal event with the most significant support for nonzero $\kappa$, the third is the most extreme representative of a class of events with bimodal $\kappa$ posteriors, and the third shows signs of potential noise anomalies.
Through these examples, we elucidate some of the interactions between $\kappa$ and the source luminosity distance, inclination and spin parameters.
